\EVOSUITE at the SBST 2019 Tool Competition

### 2019-03-26 papers/sbst19/paper_sbst19.tex
Update text

The effectiveness of \EVOSUITE has been evaluated on open source as well as industrial software in terms of code coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa}, fault finding
effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and software maintenance~\cite{ICST2018_Maintenance}.

\EVOSUITE has a longstanding record of success at the unit testing
tool competition, having ranked second in the third edition of the
competition~\cite{evosuiteAtSbst2015} and first in all the other
editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017,evosuiteAtSbst2018}.

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:t3_results}Detailed results of \TT on the
    SBST benchmark classes.}
\vspace{-1em}
\resizebox{\textwidth}{!}{  
\input{mainTable-t3.tex}
}	
\end{table*}

@@

\paragraph{Overall Results}

\TODO{}

@@

\paragraph{Flaky Tests}

\TODO{}

@@

\paragraph{Problematic benchmarks}

\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2, SPOON-169,
SPOON-25, and WEBMAGIC-4, and generally struggled with most AUTHZFORCE
benchmarks (highlighted in grey in Table~\ref{table:results}).

The benchmarks DUBBO-2 and WEBMAGIC-4 had missing dependencies in the
competition setup~\cite{sbst19competition} (something we reported last
year~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was incapable of
generating any test: When a dependency of the class under test is missing, then
\EVOSUITE intentionally aborts with an error to inform the user of the
configuration error. While this is desirable behavior during regular usage,
arguably in the scope of the competition \EVOSUITE could try to ignore such
errors and try to generate tests nevertheless, as it might still be possible to
cover code even with some missing dependencies. For the benchmark FASTJSON-3 and
a 10s time budget, \EVOSUITE generated some test suites but due to a bug in the
competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure

@@

For a 10 seconds time budget, Table~\ref{table:results} reports ``-'' for
benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and SPOON-105.
% last message in the log files was * Initial Number of Goals in DynMOSA = 942 / 10337
\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
be used in this benchmarks with a time budget of 10s.}
%
On the other hand, and surprisingly, for benchmarks SPOON-155, SPOON-16,
SPOON-20, and SPOON-211, \EVOSUITE successfully generated test suites for small
time budgets but it failed to do it for large time budgets. For all, \EVOSUITE
crashed due to a bug in the DynaMOSA algorithm.
%% SPOON-155 (240s), SPOON-16 (120s), SPOON-20 (120s and 240s), SPOON-211 (120s)
%java.lang.NullPointerException: null
%	at org.evosuite.ga.operators.ranking.RankBasedPreferenceSorting.getNumberOfSubfronts(RankBasedPreferenceSorting.java:158) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.ga.metaheuristics.mosa.DynaMOSA.generateSolution(DynaMOSA.java:152) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.strategy.MOSuiteStrategy.generateTests(MOSuiteStrategy.java:115) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.  This project has been funded by the EPSRC project
``GREATEST'' (EP/N023978/2), and by the National Research Fund,
Luxembourg (FNR/P10/03). \TODO{update}

>>>>

In the past, the effectiveness of \EVOSUITE has been evaluated on open
source as well as industrial software in terms of code
coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa},
fault finding
effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and
software maintenance~\cite{ICST2018_Maintenance}.
%
\EVOSUITE has a longstanding record of success at the unit testing
tool competition, having ranked second in the third edition of the
competition~\cite{evosuiteAtSbst2015} and first in all the other
editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017,evosuiteAtSbst2018}.

@@

%\begin{table*}[t]
%  \centering
%  \caption{\label{table:t3_results}Detailed results of \TT on the
%    SBST benchmark classes.}
%\vspace{-1em}
%\resizebox{\textwidth}{!}{  
%\input{mainTable-t3.tex}
%}	
%\end{table*}

@@

%\paragraph{Overall Results}

@@

@@

On the whole, the performance of \EVOSUITE was in line with previous
results, although \EVOSUITE seemed to fail on a notably large number
of classes. In particular, \EVOSUITE failed to produce any test
suites for benchmarks DUBBO-2, SPOON-169, SPOON-25, and WEBMAGIC-4,
and generally struggled with most AUTHZFORCE benchmarks (highlighted
in grey in Table~\ref{table:results}).

A closer look at the benchmarks DUBBO-2 and WEBMAGIC-4 reveals that
there were missing dependencies in the competition
setup~\cite{sbst19competition} (similar to cases in previous
years~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was
incapable of generating any test: When a dependency of the class
under test is missing, then \EVOSUITE intentionally aborts with an
error to inform the user of the configuration error. While this is
desirable behavior during regular usage, arguably in the scope of the
competition \EVOSUITE could try to ignore such errors and try to
generate tests nevertheless, as it might still be possible to cover
code even with some missing dependencies. For the benchmark
FASTJSON-3 and a 10s time budget, \EVOSUITE generated some test
suites but due to a bug in the
competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure

@@

In general, \EVOSUITE often struggles with a time budget as low as 10
seonds. For example, Table~\ref{table:results} reports ``-'' for
benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and
SPOON-105.
% last message in the log files was * Initial Number of Goals in DynMOSA = 942 / 10337
%\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
%be used in this benchmarks with a time budget of 10s.}
%
Surprisingly, for benchmarks SPOON-155, SPOON-16, SPOON-20, and
SPOON-211, \EVOSUITE successfully generated test suites for small
time budgets but it failed to do it for large time budgets. For all,
\EVOSUITE crashed due to a bug in the DynaMOSA algorithm which had
not been revealed by our previous experiments. Consequently, even
though DynaMOSA is known to increase the coverage \EVOSUITE achieves
subtantially in general, this increase was countered with some
missing datapoints. As always, the competition was helpful in
improving the robustness of the tool, by revealing this and other
bugs.
%% SPOON-155 (240s), SPOON-16 (120s), SPOON-20 (120s and 240s), SPOON-211 (120s)
%java.lang.NullPointerException: null
%	at org.evosuite.ga.operators.ranking.RankBasedPreferenceSorting.getNumberOfSubfronts(RankBasedPreferenceSorting.java:158) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.ga.metaheuristics.mosa.DynaMOSA.generateSolution(DynaMOSA.java:152) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.strategy.MOSuiteStrategy.generateTests(MOSuiteStrategy.java:115) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.  This project has been funded by the EPSRC project
``GREATEST'' (EP/N023978/2), and by the National Research Fund,
Luxembourg (FNR/P10/03).
